Safe Memory Regions for Big Data Processing

### 2016-06-21 paper/type-inference.tex
type inference

\emph{Recursive Classes}.
The region parameters for a recursive class is computed in
a similar fashion, with the following difference: any recursive
field is ignored while instantiating region parameters for the fields of
the class, and the region parameters of the recursive class are computed
as before. We then do parameter instantiation for all recursive fields,
such that their region annotations (the actial region parameters) are
exactly the same as the (formal) region parameters of the class.
The following example illustrates this for a non-generic \C{List} class.
The resulting class represents a linked list with spine in the region
$\rho_0$ and data objects in the region $\rho_1$.

@@

Our constraints also make uses of \emph{pending substitutions}\footnote{we borrowed this terminology from~\cite{ltpldi08}} $F$.
A pending substitution serves to bind formal region parameters in $\varphi$ to the actual region parameters
used in a particular context:
\begin{smathpar}
\begin{array}{lcl}
F & \coloneqq & \cdot \ALT [\rho/\rho]F \\
\end{array}
\end{smathpar}
E.g., in the validity constraint $\isvalid{\rgn_1 \outlives
\rgn_2}{[\rgn_1/\rho_1][\rgn_2/\rho_2]\varphi}$, the pending substitution
is $[\rgn_1/\rho_1][\rgn_2/\rho_2]$. Any concrete formula (call it
$\phisol$) over variables $\rho_1$ and $\rho_2$ is a solution to
$\varphi$ if and only the formula obtained by substituting $\rgn_1$
and $\rgn_2$ for $\rho_1$ and $\rho_2$ (resp.) in $\phisol$ is
deducible from $\rgn_1 \outlives \rgn_2$.

@@

>>>>

\emph{Recursive Classes}.
The region parameters for a recursive class is computed in
a similar fashion, with the following difference: any recursive
field is ignored while instantiating region parameters for the fields of
the class, and the region parameters of the recursive class are computed
as before. We then do parameter instantiation for all recursive fields,
such that their region annotations (the actual region parameters) are
exactly the same as the (formal) region parameters of the class.
The following example illustrates this for a non-generic \C{List} class.
The resulting class represents a linked list with spine in the region
$\rho_0$ and data objects in the region $\rho_1$.

@@

Our constraints also make uses of \emph{pending substitutions} $F$:
% \footnote{we borrowed this terminology from~\cite{ltpldi08}}
A pending substitution serves to bind formal region parameters in $\varphi$ to the actual region parameters
used in a particular context:
\begin{smathpar}
\begin{array}{lcl}
F & \coloneqq & \cdot \ALT [\rho/\rho]F \\
\end{array}
\end{smathpar}
E.g., in the validity constraint $\isvalid{\rgn_1 \outlives
\rgn_2}{[\rgn_1/\rho_1][\rgn_2/\rho_2]\varphi}$, the pending substitution
is $[\rgn_1/\rho_1][\rgn_2/\rho_2]$. Any concrete formula (call it
$\phisol$) over variables $\rho_1$ and $\rho_2$ is a solution to
$\varphi$ if and only if the formula obtained by substituting $\rgn_1$
and $\rgn_2$ for $\rho_1$ and $\rho_2$ (resp.) in $\phisol$ is
deducible from $\rgn_1 \outlives \rgn_2$.

@@

\paragraph{Soundness and Completeness.}

\textbf{TO DO:}
The entire algorithm is sound.
The second phase is complete as well: if there is any possible instantiation (of the
region variables and predicate variables) of the elaborated program produced by the first
phase that type checks, then the second phase will identify it.
Incompleteness exists only in a few choices made during the first phase (elaboration phase).
